Report

### 2022-07-20 manuscript.Rmd
update 2022-07-20 15:17:16

```{r setup, include = FALSE}
run_everything <- FALSE
library("papaja")
library(tidySEM)
library(kableExtra)
r_refs("r-references.bib")
out <- readRDS("out.RData")
```

>>>>

```{r setup, include = FALSE}
run_everything <- FALSE
library("papaja")
library(tidySEM)
library(kableExtra)
library(pwr)
r_refs("r-references.bib")
out <- readRDS("out.RData")
```
